Fast and Error-Adaptive Count-Distinct Sketch \\for Influence Maximization

### 2021-01-12 paper.tex
progress

Even though, \acro's behavior is not chaotic with respect to changes in parameters. Our method's performance, both in terms of speed and quality of results, depends on parameter selection. Setting $\epsilon_local$ to $0$ means that \acro will always rebuild sketches, which would slowdown the method but it will give the best possible results. On the other hand, setting $\epsilon_local$ to infinity will be very fast, since sketches are build only once without checking vertices blocked. But, quality of the results will suffer.

>>>>

Since, $\epsilon_local$ is the maximum error allowed after the last rebuild. Setting $\epsilon_local$ to $0$ means that \acro will always rebuild sketches, which would slowdown the method but it will give the best possible results. Conversely, setting $\epsilon_local$ to infinity will be very fast, since sketches are build only once without checking vertices blocked. But, the result quality will suffer. $\epsilon_global$, on the other hand, is the minimum influence we expected to obtain via building the sketch. If we were to set $\epsilon_global$ to 0, \acro will not rebuild the sketches, but when $\epsilon_global$ is set to infinity, we skill need to compare $\epsilon_local$ to estimation error before rebuilding.

Even though, \acro's behavior is not chaotic with respect to changes in parameters. Our method's performance, both in terms of speed and quality of results, depends on parameter selection. We conducted a grid search over several parameter combinations to illustrate how \acro performs with different parameters. In figure~\ref{fig:parameter-smallmultiples}, both speed and quality of results on some of the largest datasets we have experimented is shown.  We found that, the parameters $\epsilon_{local}=0.3$ and $\epsilon_{global}=0.01$ used in our experiments, performs decent in many datasets, both in terms of speed and quality.
